Title Goes Here

### 2017-09-06 analysis/paper/paper.Rmd
changed name to dynalysis
added method toys figure

library(dynanalysis)
```

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv("../data/raw_data/my_csv_file.csv")
```

>>>>

library(dynalysis)
library(tidyverse)
```

@@

```{r get-data}
scores <- read_rds("../data/derived_data/toy_method_scores.rds")

scores %>%
  dplyr::select(-starts_with("time")) %>%
  gather(score_id, score, -method_name, -method_short_name, -task_id, -error, -warning) %>%
  ggplot() + geom_bar(aes(method_name, score, fill=score_id), stat="identity") + facet_wrap(~score_id) + coord_flip()
```
